\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\setlist{noitemsep}
\usepackage{color}
\usepackage{array}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[compact]{titlesec}
\titlespacing*{\section}{0pt}{6pt}{6pt}
\titlespacing*{\subsection}{0pt}{6pt}{6pt}

\begin{document}
\thispagestyle{empty}

\begin{center}
\textbf{Team AnotherOne \qquad Project Mytinerary \\ Minutes for Meeting}
\vspace{0.33cm}
\end{center}

\textbf{Date and Time:} January 29 1:00 PM \\
\textbf{Location:} H961-26 \\

\begin{center}
\begin{tabular}{| m{4cm} | m{4cm} |} \hline
\textbf{Members} & \textbf{Present} \\ \hline
Annamalai, Piratheeban & Yes \\ \hline
Lam, Laurendy          & Yes \\ \hline
Luo, Jacqueline        & No  \\ \hline
Mescheder, Michael     & Yes \\ \hline
Nguyen, Andy           & Yes \\ \hline
Nguyen, Kenny          & No  \\ \hline
Pang, Ronn             & Yes \\ \hline
Payette, Eric          & Yes \\ \hline
Power, Alessandro      & Yes \\ \hline
Talarico, James        & Yes \\ \hline
Velauthapillai, Pragas & Yes \\ \hline
Vu-Nguyen, Anhkhoi     & Yes \\ \hline
\end{tabular}
\end{center}

\subsection*{Minutes of the Meeting}
\subsubsection*{Discussion}
\begin{itemize}
    \item Possible survey questions were put forth and critiqued.
    \item The fact that the app would be 3rd party, rather than a Concordia
    affiliated app, was brought up. This implies that Mytinerary would not have
    access to a student records database, for example.
    \item ENCS 282 requires \emph{either} passing ENCS 272 or passing the EWT; this
    would have to be implemented.
    \item The possibility of using "sliders" to indicate student preferences was
    brought up; this would allow the schedule to present more desirable schedules first.
\end{itemize}

\subsubsection*{Decisions}
\begin{itemize}
    \item Survey would be completed for Monday, at which point the documentation
    team would begin distributing them.
    \item Student account creation would have to be modified in order to allow
    student's to enter their academic record.
    \item Drafts of deliverable 1 sections (minus planning and protoyping) would be
    completed for Wednesday.
\end{itemize}

\subsection*{\color{red}{Next Meeting: Friday February 5}}

\end{document}